---
title: "BIO8940 course"
description: |
  Open science and advanced biostatistics course. A grad student level course at the University of Ottawa.
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```


Who: [Julien Martin](https://juliengamartin.github.io/)  
When: 1430-1720 on Tuesdays (Winter 2024)  
Where: CRC-C316  

# Course info

* [Lecture slides](slides.html)
* [Practical manual](https://bio8940-uottawa.github.io/class_book/)
* Syllabus ([english](syllabus_en.html) and [french](syllabus_fr.html))


# Requirements

<!-- * Download and install [Git](https://git-scm.com/downloads). -->

* You will need a GitHub account, you can easily set up a free account [here](https://github.com/).

* Install [`R`](https://cloud.r-project.org/) and your favourite R IDE [`RStudio`](https://rstudio.com/products/rstudio/download/#download) or [`VSCode`](https://code.visualstudio.com/Download)

<!-- * Have Git, GitHub and RStudio talk to each other following [these guidelines (section 2.2.2 Configuration only)](https://inbo.github.io/git-course/course_rstudio.html#222_configuration). -->

<!-- * Install the following `R` packages: `tidyverse`, `sf`, `emo`, `janitor`, `palmerpenguins`, `usethis` and `lubridate.` You can install them all at once by running the following code in the `R` command line: -->

```{r eval = FALSE, echo = FALSE}
install.packages(c("tidyverse", "sf", "emo", "janitor", "palmerpenguins", "usethis", "lubridate"))
```

## Corrections {.appendix}

If you see mistakes or want to suggest changes, please [create an issue](https://github.com/BIO8940-uOttawa/Course_material/issues) on the source repository.

## Reuse {.appendix}

Text and figures are licensed under Creative Commons Attribution [CC BY 4.0](https://creativecommons.org/licenses/by/4.0/). Any computer code (R, HTML, CSS, etc.) in slides and worksheets, including in slide and worksheet sources, is also licensed under [MIT](https://github.com/BIO8940-uOttawa/Course_material/blob/master/LICENSE.md). 

