---
title: | 
  Advanced statistics and Open science
format:
  html:
    toc: false
---

{{< include _links.qmd >}}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r timing, echo = FALSE}
start <- 1430
stop <- 1720
where <- "CRX-C323"
```

 This is a graduate level class at the University of Ottawa

Who: [Julien Martin](people.qmd)  
When: `r start`-`r stop` on Tuesdays (Winter 2024)  
Where: `r where`

# Course info

* [Course content (lectures & notes)](lectures.qmd)
* [Practical manual][manual_8940]
* [Syllabus](syllabus.qmd)

# Open science resources

I developed proposal and thesis templates that are 1) useable directly as Quarto a extension, 2) provide brief explanation of the expected content of each section, and 3) generate pdf documents appropriately formatted for uOttawa requirements (at least biology)

* [bio-uo-proposal](https://github.com/JulienGAMartin/quarto-bio-uo-proposal) quarto extension providing 1 new pdf output format (`bio-uo-proposal-pdf`). I am working on a docx version but tweaking the frontpage is tricky with word document. 

* [bio-uo-thesis](https://github.com/JulienGAMartin/quarto-bio-uo-thesis): quarto extension  providing two new output formats for book projects: an html (`bio-uo-thesis-html`) and a pdf (`bio-uo-thesis-pdf`) generating a website (to be hosted on github pages or similar) and a pdf of the thesis adequately formatted for uOttawa (at least biology)



# Requirements

<!-- * Download and install [Git](https://git-scm.com/downloads). -->

* a GitHub account. (Set up a free account [here](https://github.com/)).

* [`R`][cran] and your favourite R IDE [`RStudio`][rstudio_d] or [`VSCode`][vscode_d]

* [`git`][git_install] software

* [`quarto`][quarto_install] software

<!-- * Have Git, GitHub and RStudio talk to each other following [these guidelines (section 2.2.2 Configuration only)](https://inbo.github.io/git-course/course_rstudio.html#222_configuration). -->

<!-- * Install the following `R` packages: `tidyverse`, `sf`, `emo`, `janitor`, `palmerpenguins`, `usethis` and `lubridate.` You can install them all at once by running the following code in the `R` command line: -->

```{r eval = FALSE, echo = FALSE}
install.packages(c("tidyverse", "sf", "emoji", "janitor", "palmerpenguins", "usethis", "lubridate"))
```

--------------------------------------------------------------------------------

#### Corrections {-}

If you see mistakes or want to suggest changes, please [create an issue](https://github.com/biostats-uOttawa/bio8940-course/issues) on the source repository.

#### Reuse {-}

Text and figures are licensed under Creative Commons Attribution [CC BY 4.0](https://creativecommons.org/licenses/by/4.0/). Any computer code (R, HTML, CSS, etc.) in slides and worksheets, including in slide and worksheet sources, is also licensed under [MIT](https://github.com/biostats-uOttawa/bio8940_course/blob/master/LICENSE.md). 

