---
title: "Advanced statistics and Open science"
output:
  html_document:
    toc: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
 This is a graduate level class at the University of Ottawa

Who: [Julien Martin][lab_website]  
When: 1430-1720 on Tuesdays (Winter 2024)  
Where: CRX - C323

# Course info

* [Lecture slides](lectures.html)
* [Practical manual][manual]
* [Syllabus](syllabus.html)


# Requirements

<!-- * Download and install [Git](https://git-scm.com/downloads). -->

* You will need a GitHub account, you can easily set up a free account [here](https://github.com/).

* Install [`R`][cran] and your favourite R IDE [`RStudio`][rstudio_d] or [`VSCode`][vscode_d]

<!-- * Have Git, GitHub and RStudio talk to each other following [these guidelines (section 2.2.2 Configuration only)](https://inbo.github.io/git-course/course_rstudio.html#222_configuration). -->

<!-- * Install the following `R` packages: `tidyverse`, `sf`, `emo`, `janitor`, `palmerpenguins`, `usethis` and `lubridate.` You can install them all at once by running the following code in the `R` command line: -->

```{r eval = FALSE, echo = FALSE}
install.packages(c("tidyverse", "sf", "emo", "janitor", "palmerpenguins", "usethis", "lubridate"))
```

## Corrections {.appendix}

If you see mistakes or want to suggest changes, please [create an issue](https://github.com/BIO8940-uOttawa/Course_material/issues) on the source repository.

## Reuse {.appendix}

Text and figures are licensed under Creative Commons Attribution [CC BY 4.0](https://creativecommons.org/licenses/by/4.0/). Any computer code (R, HTML, CSS, etc.) in slides and worksheets, including in slide and worksheet sources, is also licensed under [MIT](https://github.com/BIO8940-uOttawa/Course_material/blob/master/LICENSE.md). 

```{r links, child="links.md", include = FALSE}
```