---
title: "Lectures"
---

{{< include _links.qmd >}}

```{r}
#| echo: false
#| include: false
knitr::opts_chunk$set(echo = FALSE)
source("_yaml_extract.R")
library(gt)
library(lubridate)
```

## Student presentations


 Please register for your presentations [here](https://uottawa-my.sharepoint.com/personal/jmartin8_uottawa_ca/_layouts/15/guestaccess.aspx?share=EbAUafs8KSdEhoP6xs0XqiwBG4lI6raInEKrssUN6nbm7w&e=RzBfDv).

 You need to log into your uottawa account to have access

<!-- ### Lecturer {{< fa person-chalkboard >}}  -->

```{r lecturers, results="asis", eval = FALSE, include = FALSE}
team_df %>%
  filter(role == "lecturer") %>%
  pull(name) %>%
  ui_list()
```

<!-- ## Teaching assitant`r ifelse(ntutor > 1, 's', '')`-->
```{r tutors, results="asis"}
team_df %>%
  filter(role == "tutor") %>%
  pull(name) %>%
  ui_list()
```
<!-- 
### Office hours {{< fa clock >}}

Meetings will be in-person or online using zoom. Check brightspace for the links. -->

```{r consult, results="asis", eval = FALSE, include = FALSE}
team_df %>%
  mutate(consult_print = glue::glue("**{name}**: {consult}")) %>%
  pull(consult_print) %>%
  ui_list()
```

## Schedule {{< fa calendar-days >}}

```{r timetable, results="asis"}
timetable_df %>%
  mutate(timetable = glue::glue("**{class}**: {when} in {where}")) %>%
  pull(timetable) %>%
  ui_list()
```


There are no lectures or tutorials during reading week.

```{r}
check <- character(0)
schedule_df <- schedule_df %>%
  rowwise() %>%
  mutate(
    lecture_file = ifelse(
      identical(
        str_subset(
          list.files("slides/", pattern = "slides.html", full.names = TRUE),
          pattern = sprintf("lec-%.2d", week)
        ),
        check
      ),
      NA,
      str_subset(
        list.files("slides/", pattern = "slides.html", full.names = TRUE),
        pattern = sprintf("lec-%.2d", week)
      )
    ),
    notes_file =  ifelse(
      identical(
        str_subset(
          list.files("slides/", pattern = "notes", full.names = TRUE),
          pattern = sprintf("lec-%.2d", week)
        ),
        check
      ),
      NA,
      str_subset(
        list.files("slides/", pattern = "notes", full.names = TRUE),
        pattern = sprintf("lec-%.2d", week)
      )
    ),
    lecture = !is.na(lecture_file)
  ) %>%
  ungroup() %>%
  mutate(
    Slides = case_when(
      lecture ~ glue("<a class='fa fa-display' href='{lecture_file}' target='_blank'></a> <a class='fa fa-note-sticky' href='{notes_file}' target='_blank'></a>"),
      TRUE ~ ""
    ),
    Topic = ifelse(is.na(topic), "", topic),
    Assessment = ifelse(is.na(assessment), "", assessment),
    Reading = ifelse(is.na(reading), "", reading),
    Date = as.Date(ifelse(
      (ymd(dat$date_start) + weeks(week-1)) > ymd(dat$date_read),
      ymd(dat$date_start) + weeks(week),
      ymd(dat$date_start) + weeks(week - 1)
    ))
  ) %>%
  select(Date, Topic, Slides, Reading, Assessment)

midsem_break <- 6 # after which week

read_week <- paste0()
schedule_df %>%
  gt() |>
#  cols_label(week = "Week") |>
  fmt_markdown(columns = c("Slides", "Reading")) |>
  fmt_date(
    columns = Date,
    date_style = "MMMd",
    locale = "en"
  ) |>
  tab_row_group(
    label = "Reading week",
    rows = (midsem_break + 1):12
  ) |>
  row_group_order(groups = c(NA, "Reading week")) |>
  cols_width(
    Date ~ px(50),
    Slides ~ px(20)
  )
```

## About slides {{< fa display >}} and notes {{< fa note-sticky >}}

### Slides {{< fa display >}} 

Slides in `revealjs` format (html). If you want then as a pdf (*note you might loose some functionality or contents due to tabs and scroll sections*):

1. Open the slides in your browser from a link on this page
2. Press `e` to get into the PDF export mode (*`?print-pdf` should appear near the end of the url and white borders should appear*)
1. Open the in-browser print dialog (CTRL/CMD+P).
1. Change the `Destination` setting to `Save as PDF`.
1. Change the `Layout` to `Landscape`.
1. Change the `Margins` to `None`.
1. Enable the Background graphics option (if you want it)
1. Click Save 🎉

### Notes {{< fa note-sticky >}}

Content of the slides in html format as a single contained downloadable file and including tabs and scroll sections. 

More importantly, notes have the commenting and annotateing tools activated via <https://hypothes.is/>. If you create a free account , you can annotate and comment slides as well as share your annotations/comments with the public or via private or public groups.
